---
title: "BLT Model v1 Validation Guareí"
author: "Eduardo Zanette"
date: "05/05/2022"
abstract: |

  This document was produced for the purpose of reporting validation patterns of the BLT Model. 
      
output: 
  pdf_document:
  
fontsize: 12pt
toc: yes
toc_depth: 3
number_sections: yes
# baselinestretch: 1.12
# linestretch: 1.22
# toc: yes
# toc_depth: 3
# lof: True
# lot: True
# papersize: a4
# tables: true
# number_sections: yes
---

\pagenumbering{arabic}

> Conclusions

#### The *four* problems with this model are:

1) 

\pagebreak

```{r setup, include=FALSE}
# Packages
library("knitr")
library("rmarkdown")
library("flextable") ## having nice tables working also in LibreOffice
library("officer")
library("here")
library("tidyverse")
library("ggspatial")
library("sp")
library("adehabitatHR")
library("circular")
library("nlrx")

knitr::opts_chunk$set(echo = TRUE)

# GIS
our_crs <- "+proj=utm +zone=22 +south +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
gua_xlim_all = c(780000, 782350)
gua_ylim_all = c(7407080, 7408250)
gua.x.min = 781587
gua.x.max = 782361.5
gua_xlim_set = c(781200, 782350)
gua_ylim_set = c(7407250, 7408250) 
sma_xlim_set = c(364400, 366000)
sma_ylim_set = c(7540500, 7541700)
taq_xlim_set = c(370500, 373200)
taq_ylim_set = c(7498750, 7500550)
suz_xlim_set = c(705300, 706200)
suz_ylim_set = c(7480800, 7481600) # 7480990,

# Plots
theme_set(theme_bw())
simulated_shapes <- c(1, 19, 1, 17, 1)
simulated_colors <- c("magenta", "#1E8449", "grey", "#E74C3C", "grey")
simulated_colors_noforage <- c("grey", "#1E8449", "grey", "#E74C3C", "grey")

empirical_shapes <- c(1, 19, 1, 1, 1, 1, 1, 1, 1, 17, 1, 1)
empirical_colors <- c("magenta", "#1E8449", "grey", "grey", "grey", "grey", "grey", 
                                "grey", "grey", "#E74C3C", "grey", "grey")


# Knitr
knitr::opts_chunk$set(echo = TRUE,
                      fig.align='center')
```

```{r Load shapefiles, results="hide", warning=F, echo=F, message=F}
library("sf")
gua.polyg <- sf::st_read(here("Data", "shapefiles", "Fragment polygon.shp"))
# sf::st_collection_extract(gua.polyg, type = "POLYG")
# # sf::st_filter(gua.polyg)
# gua.polyg <- gua.polyg[gua.polyg$Name == "Fragment", ]
# gua.polyg <- filter( is.na(st_dimension(gua.polyg)) == FALSE )
```

```{r Base Guarei sf plot, include=FALSE}
gua.sf <- ggplot2::ggplot() +
  geom_sf(data = gua.polyg,
          color = "black",
          fill = "#A9DFBF") +
  coord_sf(
    datum = sf::st_crs(our_crs),
    xlim = gua_xlim_set,    
    ylim = gua_ylim_set) +  
  theme_bw() +
  annotation_scale(location = "bl", width_hint = .35) +
  annotation_north_arrow(location = "bl", which_north = "true",
                         pad_x = unit(0, "cm"), pad_y = unit(.8, "cm"),
                         style = north_arrow_fancy_orienteering)
```


### Guareí empirical 

#### All data (28 days) and July only (6 days)

```{r, echo=F, warnings = F, message=F}
dat.gua.orig <- read.csv2("D:/Data/Documentos/github/BLT-Movement-Patterns/asltraj/ltraj_df_Data_Guarei_Felipe_EMZ1.csv", dec = ".", stringsAsFactors = TRUE)
dat.gua.orig <- dat.gua.orig %>%
  rename(datetime = POSIXct) %>%
  mutate(datetime = lubridate::ymd_hms(datetime))

dat.gua.orig <- dat.gua.orig %>% 
  mutate(day = lubridate::day(datetime)) %>% 
  mutate(month = lubridate::month(datetime)) %>% 
  mutate(day_month = paste0(dat.gua.orig$day, "-", dat.gua.orig$month))

gua.plot <- gua.sf +
  geom_path(data = dat.gua.orig,
            aes(x = x, y = y, group = day_month), 
            size = 0.15) +
  geom_point(data = dat.gua.orig,
             aes(x = x, y = y, group = behavior,
                 color = behavior,
                 shape = behavior), 
             size = 2.2) +
  ggtitle("Empirical (all data, 28 days)") +
  scale_shape_manual(values = c(1, 19, 1, 1, 1, 1, 1, 1, 1, 17, 1, 1)) +
  scale_color_manual(values = c("grey", "#1E8449", "grey", "grey", "grey", "grey", "grey", "grey", "grey", "#E74C3C", "grey", "grey"))
  
gua.plot

dat.gua.orig.jul <- dat.gua.orig %>% filter(month == 6)

gua.plot <- gua.sf +
  geom_path(data = dat.gua.orig.jul,
            aes(x = x, y = y, group = day_month), 
            size = 0.15) +
  geom_point(data = dat.gua.orig.jul,
             aes(x = x, y = y, group = behavior,
                 color = behavior,
                 shape = behavior), 
             size = 2.2) +
  ggtitle("Empirical (July only, 6 days)") +
  scale_shape_manual(values = c(1, 19, 1, 1, 1, 1, 17, 1, 1)) +
  scale_color_manual(values = c("grey", "#1E8449", "magenta", "grey", "grey", "grey", "#E74C3C", "grey", "grey"))
  
gua.plot
```

\pagebreak

### Guareí simulated

```{r}
# load RDS file with results from nlrx runs and unnest turtle variable
filename <- here("Model_development", "Model-cleaning", "runtime", "tempRDS.Rdata")
nl <- readRDS(filename)
results_unnest <- unnest_simoutput(nl)

# Clean memory:
rm(results)
gc()

# Check behaviors:
results_unnest$behavior %>% unique()

# Check steps, timesteps and days:
# results_unnest$`[step]` %>% unique()
# results_unnest$timestep %>% unique()
# results_unnest$day %>% unique()

```

#### Prepare simulation data
```{r}
results_unnest <- results_unnest %>% 
  rename(x = x, y = y)
```


#### One random run (10 days) (=go button)
```{r }
gua.plot.general <- gua.sf +
  geom_path(data = results_unnest,
            aes(x = x, y = y), 
            size = 0.15) +
  geom_point(data = results_unnest,
             aes(x = x, y = y, group = behavior,
                 color = behavior,
                 shape = behavior
                 ), size = 1.4) +
  scale_color_manual(values = simulated_colors) +
  scale_shape_manual(values = simulated_shapes) +
  ggtitle("Guareí - simulated (1 run, 10 days - All resources)")
gua.plot.general
```

#### One random run (1 random day) (= next_day button) all steps

```{r}
# Select random run by selecting random seed (run of x days = seed)
aux_run <- results_unnest$`random-seed` %>%
  na.exclude() %>%
  sample(size = 1)

# Select random run by selecting random seed (run of x days = seed)
aux_day <- results_unnest$`day` %>%
  na.exclude() %>%
  sample(size = 1)

# # patches
# results_unnest_patches <- results_unnest %>%
#   dplyr::filter(agent=="patches") %>%
#   # dplyr::filter(`random-seed` == aux) %>%
#   dplyr::filter( `timestep` %in% seq(8, 108, by=10)) # `[step]` instead of timestep does not work



# # # Create facet plot with different dfs (patches and turtles)
# # library(ggplot2)
# # ggplot() +
# #   facet_wrap(~`[step]`, ncol=6, nrow = 2) +
# #   coord_equal() +
# #   geom_tile(data=results_unnest_patches, aes(x=pxcor, y=pycor, fill=factor(pcolor))) +
# #   geom_point(data=results_unnest_turtles, aes(x = xcor, y = ycor, 
# #                                               group = breed, color = breed,
# #                                               size = breed, shape = breed), 
# #              size = 1) +
# #   scale_fill_manual(breaks=c("49", "68"),
# #                     values = c("49" = "#F6F9BF", "68" = "#BFF8B7")) +
# #   
# #   scale_color_manual(breaks=c("seeds", "feeding-trees", 
# #                               "sleeping-trees", "monkeys"
# #                               # "resting-trees", "seeds"
# #                               ), 
# #                      values = c("seeds" = "grey", "feeding-trees" = "green",
# #                                 "sleeping-trees" = "magenta", "monkeys" = "black"
# #                                 # "seeds" = "red"
# #                                 )) + 
# #   
# #   scale_size_manual(breaks=c("seeds", "feeding-trees", 
# #                               "sleeping-trees", "monkeys"
# #                               ),
# #                      values = c("seeds" = 0.3, "feeding-trees" = 1,
# #                                 "sleeping-trees" = 1, "monkeys" = 1.5)) +
# #   
# #   scale_shape_manual(breaks=c("seeds", "feeding-trees", 
# #                               "sleeping-trees", "monkeys"
# #                               ),
# #                     values = c("seeds" = 1, "feeding-trees" = 1,
# #                                "sleeping-trees" = 1, "monkeys" = 8)) +
# #   
# #   guides(fill=guide_legend(title="Patch color")) +
# #   theme_minimal() +
# #   ggtitle("Output maps of each 10th simulation tick")
# 
# 
# # Create animated plot (GIF)
# require(gganimate)
# p1 <- ggplot() +
#   
#   geom_tile(data=results_unnest_patches, 
#             aes(x=pxcor, y=pycor, fill=factor(pcolor))) +
#   scale_fill_manual(breaks=c("49", "68"),
#                     values = c("49" = "#F6F9BF", "68" = "#BFF8B7")) +
#   
#   geom_point(data=results_unnest_seeds, 
#              aes(x = xcor, y = ycor, group = breed), 
#              size = 0.5, color = "black", shape = 4) +
#   
#   geom_point(data=results_unnest_sleep, 
#              aes(x = xcor, y = ycor, group = breed), 
#              size = 1.5, color = "#E3A9F7", shape = 15) +
#   
#   geom_point(data=results_unnest_trees, 
#              aes(x = xcor, y = ycor, group = breed), 
#              size = 1, color = "black", shape = 23, fill = "#1FCD2B") +
#   
#   geom_point(data=results_unnest_monkeys, 
#              aes(x = xcor, y = ycor, group = breed), 
#              size = 4, color = "red", shape = 10) +
#   
#   guides(fill=guide_legend(title="Patch color")) +
#   transition_time(`[step]`) +
#   coord_equal() +
#   labs(title = 'Step: {frame_time}') +
#   theme_minimal() +
#   ggtitle("Output maps of each 10th simulation tick")
# 
# # Animate the plot and use 1 frame for each step of the model simulations
# library(gapminder)
# library(gganimate)
# library(gifski)
# 
# 
# animate(p1,
#         width=400, height=400,
#         renderer = gifski_renderer())
# anim_save("setup-for-workflow-simple_multiple-layers.gif")
# 
# animate(p1, nframes = length(unique(results_unnest_patches$`[step]`)),
#         width=400, height=400, fps=4,
#         duration = 5, renderer = gifski_renderer())
# anim_save("setup-for-workflow-simple_multiple-layers-by10.gif")
# 
# 
# ## Method 2: nl_to_points()
# results_points_x <- nl_to_points(nl, coords = "px")
# results_points_y <- nl_to_points(nl, coords = "py")
# 
# 
# 
# # Other
# nl
# eval_simoutput(nl)

```

#### One random run (1 random day) (= next_day button) each 10 steps
```{r}

# turtles (each 10 steps)
results_unnest_turtles <- results_unnest %>%
  dplyr::filter(agent=="turtles") %>%               # by agent
  dplyr::filter(`random-seed` == aux_run) %>%       # by random run (~= number of the agent = who)
  dplyr::filter(`day` == aux_day) %>%                # by random day
  dplyr::filter(`timestep` %in% seq(8, 108, by=10)) # each 10 steps

ggplot() +
  facet_wrap(~timestep) + # , ncol=6, nrow = 2
  coord_equal() +
  geom_point(data=results_unnest_turtles,
             aes(x = x, y = y, group = breed),
             size = 4
             # , color = "red", shape = 10
             ) +

  guides(fill=guide_legend(title="Patch color")) +
  theme_minimal() +
  ggtitle("Output maps of each 10th simulation tick (one run)")

# ggsave(filename = "setup-for-workflow-simple_multiple-layers.png",
       # dpi = 300, width = 30, height = 20, units = "cm")

```



#### Various runs (last steps only)

```{r}

# # turtles (only last stap)
# results_unnest_turtles <- results_unnest %>%
#   dplyr::filter(agent=="turtles") %>%            # by agent
#   dplyr::group_by(day) %>% 
#   dplyr::slice(tail(row_number(), 1))           # 10 for last 10 steps
```


***

\pagebreak

## Validation Patterns

We are not checking seed dispersal patterns now, just movement and ranging patterns.


### Dayly Path Lenght (DPL)

Calculate and plot DPL
```{r DPL function, echo = FALSE, }
dpl <- function(df) {
  dist_list <- numeric()
  dist <- numeric()
  for (df in split(df, df$day)) {
    dist <- 0
    for (i in 2:nrow(df)) {
      dist <- dist + sqrt((df$x[i] - df$x[i - 1]) ^ 2 +
                            (df$y[i] - df$y[i - 1]) ^ 2)
    }
    dist_list <- c(dist_list, dist)
  }
  return(dist_list)
}
```

```{r, echo=FALSE}
dpl_gua_jul <- dpl(df = dat.gua.orig.jul)

avg_dist_jul <- mean(dpl_gua_jul)
sd_dist_jul <- sd(dpl_gua_jul)
# paste("Empirical (July, 6 days) Mean DPL (m)", round(avg_dist, 2))
# paste("Empirical (July, 6 days) DPL sd", round(sd_dist, 2))

dat.gua.all <- dat.gua.orig %>% 
  rename(day_num = day) %>% 
  rename(day = burst)
dpl_gua <- dpl(df = dat.gua.all)

avg_dist <- mean(dpl_gua)
sd_dist <- sd(dpl_gua)

dpl_sim <- dpl(df = results_unnest)

avg_dist_sim <- mean(dpl_sim)
sd_dist_sim <- sd(dpl_sim)
# paste("Simulated (July, 30 days) Mean DPL (m)", round(avg_dist_sim, 2))
# paste("Simulated (July, 30 days) DPL sd", round(sd_dist_sim, 2))

# loc_tam_lastdays <- results_unnest %>% filter(day > 10) 
# dpl_sim_lastdays <-results_unnest %>% dpl()

# avg_dist_sim_lastdays <- mean(dpl_sim_lastdays)
# sd_dist_sim_lastdays <- sd(dpl_sim_lastdays)
# paste("Simulated (July, 20 days) Mean DPL (m) after burn-in run of 10 days", round(avg_dist_sim_lastdays, 2))
# paste("Simulated (July, 20 days) DPL sd after burn-in run of 10 days", round(sd_dist_sim_lastdays, 2))
```

```{r, include=FALSE}
hist_f <- function(x = x, main = main, xlab = xlab) {
  hist(x, 
       # xlab = "Daily Path Length (m)",
       xlab = xlab,
                           breaks=seq(500,12000,by=200),
                           ylim = c(0,6),
                           col = "grey",
                           main = main)
  }
```

```{r, echo=F}
par(xpd=TRUE)
par(oma=c(0,0,0,0))
par(mar=c(4,4,2,1))
par(mfrow=c(3,1))


hist <- hist_f(x=dpl_gua_jul,
     main = "Empirical (July, 6 days)",
     xlab = ""
     )
abline(v=avg_dist_jul, col="red", lty=2)
text(x=min(hist$breaks), y=max(hist$counts)
   , sprintf("sd = %7.2f", sd_dist_jul)
   , adj = c(0, 0))
text(x=avg_dist_jul, y=max(hist$counts)
   , sprintf("mean = %7.2f", avg_dist_jul)
   , col = "red"
   , adj = c(0, -0.8))


hist <- hist_f(x=dpl_gua,
             main="Empirical (All months, 28 days)",
             xlab=""
     )
abline(v=avg_dist, col="red", lty=2)
text(x=min(hist$breaks), y=max(hist$counts)
   , sprintf("sd = %7.2f", sd_dist)
   , adj = c(0, 0))
text(x=avg_dist, y=max(hist$counts)
   , sprintf("mean = %7.2f", avg_dist)
   , col = "red"
   , adj = c(0, -0.8))


hist <- hist_f(x=dpl_sim,
             main="Simulated (July, 30 days)",
             xlab = "Daily Path Length (m)"
     )
abline(v=avg_dist_sim, col="red", lty=2)
text(x=min(hist$breaks), y=max(hist$counts)
   , sprintf("sd = %7.2f", sd_dist_sim)
   , adj = c(0, 0))
text(x=avg_dist_sim, y=max(hist$counts)
   , sprintf("mean = %7.2f", avg_dist_sim)
   , col = "red"
   , adj = c(0, -0.8))


```

\pagebreak

### Home Range
Still to be done
Comparison between methods: https://doi.org/10.1111/2041-210X.13786

\pagebreak

### Turning Angles and Step Lenghts
```{r, include=FALSE}
dat.gua.orig.jul$id <- "Guareí Empirical"
dat.gua.orig.jul$id <- as.factor(dat.gua.orig.jul$id)
dat.gua.orig.jul$dayfct <- as.factor(paste("Day ", dat.gua.orig.jul$day))

dat.gua.orig.jul_ltraj <- adehabitatLT::as.ltraj(xy = dat.gua.orig.jul[, c("x", "y")], 
                                       id = dat.gua.orig.jul$id,
                                       burst = dat.gua.orig.jul$dayfct,
                                       proj4string = CRS(our_crs),
                                       typeII = FALSE,
                                       infolocs = dat.gua.orig.jul[ , c("behavior", "dayfct")]
                                       )
# Type I (time not recorded) -> OK. Infolocs -> OK
dat.gua.orig.jul_ltraj_df <- ld(dat.gua.orig.jul_ltraj) # Transform to df


loc_tam$id <-  "Guareí Simulated" 
loc_tam$id <- as.factor(loc_tam$id)
loc_tam$dayfct <- as.factor(paste("Day ", loc_tam$day))

loc_tam_ltraj <- adehabitatLT::as.ltraj(xy = loc_tam[, c("x", "y")], 
                                       id = loc_tam$id,
                                       burst = loc_tam$dayfct,
                                       proj4string = CRS(our_crs),
                                       typeII = FALSE,
                                       infolocs = loc_tam[ , c(1:3, 6, 8:10)]
                                       )
# Type I (time not recorded) -> OK. Infolocs -> OK
loc_tam_ltraj_df <- ld(loc_tam_ltraj) # Transform to df

loc_tam_lastdays$id <-  "Guareí Simulated after burn-in run" 
loc_tam_lastdays$id <- as.factor(loc_tam_lastdays$id)
loc_tam_lastdays$dayfct <- as.factor(paste("Day ", loc_tam_lastdays$day))

loc_tam_lastdays_ltraj <- adehabitatLT::as.ltraj(xy = loc_tam_lastdays[, c("x", "y")], 
                                       id = loc_tam_lastdays$id,
                                       burst = loc_tam_lastdays$dayfct,
                                       proj4string = CRS(our_crs),
                                       typeII = FALSE,
                                       infolocs = loc_tam_lastdays[ , c(1:3, 6, 8:10)]
                                       )
# Type I (time not recorded) -> OK. Infolocs -> OK
loc_tam_lastdays_ltraj_df <- ld(loc_tam_lastdays_ltraj) # Transform to df

```

```{r Mean step lenght and turning angles, warning=FALSE, echo=F}
# mean rel angle (degrees)
paste("Empirical (July, 6 d) Mean Relative Angle (degrees) = ", 
      dat.gua.orig.jul_ltraj_df$rel.angle %>%
        mean(na.rm = T) %>% round(2))

paste("Simulated (July, 30 d) Mean Relative Angle (degrees)", 
      loc_tam_ltraj_df$rel.angle %>%
        mean(na.rm = T )%>% round(2))
      
paste("Simulated (July, 20 d, after burn-in run of 10 days) Mean Relative Angle (degrees)", 
      loc_tam_lastdays_ltraj_df$rel.angle %>%
        mean(na.rm = T) %>% round(2))

# mean rel angle (radians)
dat.gua.orig.jul_ltraj_df$rel.angle.rad <- dat.gua.orig.jul_ltraj_df$rel.angle * (180 / pi)
loc_tam_ltraj_df$rel.angle.rad <- loc_tam_ltraj_df$rel.angle * (180 / pi)
loc_tam_lastdays_ltraj_df$rel.angle.rad <- loc_tam_lastdays_ltraj_df$rel.angle * (180 / pi)

dat.gua.orig.jul_ltraj_df_ra_mean <- dat.gua.orig.jul_ltraj_df$rel.angle.rad %>%  mean(na.rm = TRUE)
loc_tam_ltraj_df_ra_mean <- loc_tam_ltraj_df$rel.angle.rad %>% mean(na.rm = TRUE)
loc_tam_lastdays_ltraj_df_ra_mean <- loc_tam_lastdays_ltraj_df$rel.angle.rad %>% mean(na.rm = TRUE)

paste("Mean Relative Angle (degrees) :", dat.gua.orig.jul_ltraj_df_ra_mean)
paste("Mean Relative Angle (degrees) :", loc_tam_ltraj_df_ra_mean)
paste("Mean Relative Angle (degrees) :", loc_tam_lastdays_ltraj_df_ra_mean)


# mean step lenght
paste("Mean Step lenght (meters) :", dat.gua.orig.jul_ltraj_df$dist %>% mean(na.rm = T))
paste("Mean Step lenght (meters) :", loc_tam_ltraj_df$dist %>% mean(na.rm = T))
paste("Mean Step lenght (meters) :", loc_tam_lastdays_ltraj_df$dist %>% mean(na.rm = T))
```

```{r Plot Step lenght + turnig angles, echo=F, warning=FALSE}
# Plot Step lengh
par(mfrow=c(1,3))
graphics::hist(dat.gua.orig.jul_ltraj_df$dist, 
               # breaks=10, 
               xlim = c(0, 400), ylim = c(0, 1000),
               xlab = "Step length (m)", main = "\nEmpirical (July, 6 d)") %>%
  abline(v = mean(dat.gua.orig.jul_ltraj_df$dist, na.rm = TRUE), col = "red", lwd = 3)
  text(200, 400, paste("mean = ", round(mean(dat.gua.orig.jul_ltraj_df$dist, na.rm = TRUE), 2), 
                      " m"), cex = 1.4)
  
graphics::hist(loc_tam_ltraj_df$dist, 
               # breaks=10, 
               xlim = c(0, 400), ylim = c(0, 1000),
               xlab = "Step length (m)", main = "\nSimulated (July, 30 d)")  %>%
  abline(v = mean(loc_tam_ltraj_df$dist, na.rm = TRUE), col = "red", lwd = 3)
  text(200, 400, paste("mean = ", round(mean(loc_tam_ltraj_df$dist, na.rm = TRUE), 2), 
                      " m"), cex = 1.4)
  
graphics::hist(loc_tam_lastdays_ltraj_df$dist, 
               # breaks=10, 
               xlim = c(0, 400), ylim = c(0, 1000),
               xlab = "Step length (m)", main = "\nSimulated (July, 20 d, \nafter burn-in run of 10 days)")  %>%
  abline(v = mean(loc_tam_lastdays_ltraj_df$dist, na.rm = TRUE), col = "red", lwd = 3)
  text(200, 400, paste("mean = ", round(mean(loc_tam_lastdays_ltraj_df$dist, na.rm = TRUE), 2), 
                      " m"), cex = 1.4)


# Plot Turning angles
par(mfrow=c(1,3))

circular::rose.diag(dat.gua.orig.jul_ltraj_df$rel.angle, bins=30, prop=2.5, units = "degrees",
                    tol = 0, main = "\nEmpirical (July, 6 d)", cex = 1.2, shrink = 1.2, ticks = F)
circular::rose.diag(loc_tam_ltraj_df$rel.angle, bins=30, prop=2.5, units = "degrees", tol = 0,                      main = "\nSimulated (July, 30 d)", 
                    cex = 1.2, shrink = 1.2, ticks = F)
circular::rose.diag(loc_tam_lastdays_ltraj_df$rel.angle, bins=30, prop=2.5, units = "degrees",
                    tol = 0, main = "\nSimulated (July, 20 d, \nafter burn-in run of 10 days)",
                    cex = 1.2, shrink = 1.2, ticks = F)

```

\pagebreak

### Revisitations (coming soon)


***

\pagebreak

## Foraging in empirical data and simulated runs
```{r}
gua.plot <- gua.sf +
  geom_path(data = dat.gua.orig.jul,
            aes(x = x, y = y, group = day_month), 
            size = 0.15) +
  geom_point(data = dat.gua.orig.jul,
             aes(x = x, y = y, group = behavior,
                 color = behavior,
                 shape = behavior), 
             size = 2.7) +
  ggtitle("Empirical (July only, 6 days)") +
  scale_shape_manual(values = c(1, 19, 1, 1, 1, 1, 17, 1, 1)) +
  scale_color_manual(values = c("grey", "#1E8449", "grey", "magenta", "grey", "grey", "#E74C3C", "grey", "grey"))
  
gua.plot


dat.gua.orig <- dat.gua.orig %>% 
  mutate(day = lubridate::day(datetime)) %>% 
  mutate(month = lubridate::month(datetime)) %>% 
  mutate(day_month = paste0(dat.gua.orig$day, "-", dat.gua.orig$month))

gua.plot <- gua.sf +
  geom_path(data = dat.gua.orig,
            aes(x = x, y = y, group = day_month), 
            size = 0.15) +
  geom_point(data = dat.gua.orig,
             aes(x = x, y = y, group = behavior,
                 color = behavior,
                 shape = behavior), 
             size = 2.7) +
  ggtitle("Empirical (all data, 28 days)") +
  scale_shape_manual(values = c(1, 19, 1, 1, 1, 1, 1, 1, 1, 17, 1, 1)) +
  scale_color_manual(values = c("grey", "#1E8449", "grey", "magenta", "grey", "grey", "grey", "grey", "grey", "#E74C3C", "grey", "grey"))
  
gua.plot


gua.plot <- gua.sf +
  geom_path(data = loc_tam %>% filter(day <= 6),
            aes(x = x, y = y, group = day), 
            size = 0.15) +
  geom_point(data = loc_tam %>% filter(day <= 6),
             aes(x = x, y = y, group = behavior,
                 color = behavior,
                 shape = behavior)) +
  ggtitle("Simulated (first 6 days - Resources from July)") +
  scale_shape_manual(values = simulated_shapes) +
  scale_color_manual(values = simulated_colors)

gua.plot

gua.plot <- gua.sf +
  geom_path(data = loc_tam %>% filter(day > 10 & day < 17),
            aes(x = x, y = y, group = day), 
            size = 0.15) +
  geom_point(data = loc_tam %>% filter(day > 10 & day < 17),
             aes(x = x, y = y, group = behavior,
                 color = behavior,
                 shape = behavior)) +
  ggtitle("Simulated (6 days after burn in of 10 days - Resources from July)") +
  scale_shape_manual(values = simulated_shapes) +
  scale_color_manual(values = simulated_colors)
  
gua.plot

```

