---
title: "BLT Model v1 Validation Guareí"
author: "Eduardo Zanette"
date: "11/05/2022"
abstract: |

  This document was produced for the purpose of reporting validation patterns of the BLT Model. The graphs also were used for the presentation for the Wiegand EcoMod group on May 12th. 
      
output: 
  pdf_document:
  
fontsize: 12pt
toc: yes
toc_depth: 3
number_sections: yes
# baselinestretch: 1.12
# linestretch: 1.22
# toc: yes
# toc_depth: 3
# lof: True
# lot: True
# papersize: a4
# tables: true
# number_sections: yes
---

\pagenumbering{arabic}

> Conclusions

#### The *four* problems with this model are:

1) 

\pagebreak

```{r setup, include=FALSE}
# Packages
library("knitr")
library("rmarkdown")
library("flextable") ## having nice tables working also in LibreOffice
library("officer")
library("here")
library("tidyverse")
library("ggspatial")
library("sp")
library("sf")
library("adehabitatHR")
library("circular")
library("nlrx")

knitr::opts_chunk$set(echo = TRUE)

# GIS
our_crs <- "+proj=utm +zone=22 +south +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
gua_xlim_all = c(780000, 782350)
gua_ylim_all = c(7407080, 7408250)
gua.x.min = 781587
gua.x.max = 782361.5
gua_xlim_set = c(781200, 782350)
gua_ylim_set = c(7407250, 7408250) 
sma_xlim_set = c(364400, 366000)
sma_ylim_set = c(7540500, 7541700)
taq_xlim_set = c(370500, 373200)
taq_ylim_set = c(7498750, 7500550)
suz_xlim_set = c(705300, 706200)
suz_ylim_set = c(7480800, 7481600) # 7480990,

# Plots
theme_set(theme_bw(base_size = 14))

simulated_shapes <- c("foraging" = 1,
                      "frugivory" = 19, 
                      "resting" = 1, 
                      "sleeping" = 17, 
                      "travel" = 1)

simulated_colors <- c("foraging" = "magenta",
                      "frugivory" = "#1E8449", 
                      "resting" = "grey", 
                      "sleeping" = "#E74C3C", 
                      "travel" = "grey")

simulated_colors_noforage <- c("grey", "#1E8449", "grey", "#E74C3C", "grey")

empirical_shapes <- c(1, 19, 1, 1, 1, 1, 1, 1, 1, 17, 1, 1)
empirical_colors <- c("magenta", "#1E8449", "grey", "grey", "grey", "grey", "grey", 
                                "grey", "grey", "#E74C3C", "grey", "grey")


# Functions
hist_f <- function(x = x, main = main, xlab = xlab) {
  hist(x, 
       # xlab = "Daily Path Length (m)",
       xlab = xlab,
                           breaks=seq(0,12000,by=200),
                           ylim = c(0,6),
                           col = "grey",
                           main = main)
  }

# Knitr
knitr::opts_chunk$set(echo = TRUE,
                      fig.align='center')
```

```{r Load shapefiles, include=F, results="hide", warning=F, echo=F, message=F}
gua.polyg <- sf::st_read(here("Data", "shapefiles", "Fragment polygon.shp"))
# sf::st_collection_extract(gua.polyg, type = "POLYG")
# # sf::st_filter(gua.polyg)
# gua.polyg <- gua.polyg[gua.polyg$Name == "Fragment", ]
# gua.polyg <- filter( is.na(st_dimension(gua.polyg)) == FALSE )
```

```{r Base Guarei sf plot, include=FALSE}
gua.sf <- ggplot2::ggplot() +
  geom_sf(data = gua.polyg,
          color = "black",
          fill = "#A9DFBF") +
  coord_sf(
    datum = sf::st_crs(our_crs),
    xlim = gua_xlim_set,    
    ylim = gua_ylim_set) +  
  theme_bw() +
  annotation_scale(location = "bl", width_hint = .35) +
  annotation_north_arrow(location = "bl", which_north = "true",
                         pad_x = unit(0, "cm"), pad_y = unit(.8, "cm"),
                         style = north_arrow_fancy_orienteering)
```


## Guareí empirical

#### All data (28 days) and July only (6 days) ####

```{r, echo=F, warnings = F, message=F}
dat.gua.orig <- read.csv2("D:/Data/Documentos/github/BLT-Movement-Patterns/asltraj/ltraj_df_Data_Guarei_Felipe_EMZ1.csv", dec = ".", stringsAsFactors = TRUE)
dat.gua.orig <- dat.gua.orig %>%
  rename(datetime = POSIXct) %>%
  mutate(datetime = lubridate::ymd_hms(datetime))

dat.gua.orig <- dat.gua.orig %>% 
  mutate(day = lubridate::day(datetime)) %>% 
  mutate(month = lubridate::month(datetime)) %>% 
  mutate(day_month = paste0(dat.gua.orig$day, "-", dat.gua.orig$month))

gua.plot <- gua.sf +
  geom_path(data = dat.gua.orig,
            aes(x = x, y = y, group = day_month), 
            size = 0.15) +
  geom_point(data = dat.gua.orig,
             aes(x = x, y = y, group = behavior,
                 color = behavior,
                 shape = behavior), 
             size = 2.2) +
  ggtitle("Empirical (all data, 28 days)") +
  scale_shape_manual(values = c(1, 19, 1, 1, 1, 1, 1, 1, 1, 17, 1, 1)) +
  scale_color_manual(values = c("grey", "#1E8449", "grey", "grey", "grey", "grey", "grey", "grey", "grey", "#E74C3C", "grey", "grey"))
  
gua.plot

dat.gua.orig.jul <- dat.gua.orig %>% filter(month == 6)

gua.plot <- gua.sf +
  geom_path(data = dat.gua.orig.jul,
            aes(x = x, y = y, group = day_month), 
            size = 0.15) +
  geom_point(data = dat.gua.orig.jul,
             aes(x = x, y = y, group = behavior,
                 color = behavior,
                 shape = behavior), 
             size = 2.2) +
  ggtitle("Empirical (July only, 6 days)") +
  scale_shape_manual(values = c(1, 19, 1, 1, 1, 1, 17, 1, 1)) +
  scale_color_manual(values = c("grey", "#1E8449", "magenta", "grey", "grey", "grey", "#E74C3C", "grey", "grey"))
  
gua.plot
```

\pagebreak

## Guareí simulated

```{r}
# load RDS file with results from nlrx runs and unnest turtle variables
filename <- here("Model_analysis", "Workflow", "Run_travelspeedvar", "tempRDS.Rdata")
nl <- readRDS(filename)
results_unnest <- unnest_simoutput(nl)

# Clean memory:
rm(results)
rm(nl)
gc()

# Check behaviors:
results_unnest$behavior %>% unique()

# Check steps, timesteps and days:
# results_unnest$`[step]` %>% unique()
# results_unnest$timestep %>% unique()
# results_unnest$day %>% unique()

```

#### Prepare simulation data
```{r}
results_unnest <- results_unnest %>% 
  rename(x = x_UTM, y = y_UTM)
```


#### One random run (10 days) (=go button)
```{r }
# Select random run by selecting random seed (run of x days = seed)
aux_run <- results_unnest$`random-seed` %>%
  na.exclude() %>%
  sample(size = 1)

aux_spd <- results_unnest$travel_speed_val %>%
  na.exclude() %>%
  sample(size = 1)

results_unnest_turtles <- results_unnest %>%
  dplyr::filter(agent=="turtles") %>%               # by agent
  dplyr::filter(`random-seed` == aux_run) %>%       # by random run (~= number of the agent = who)
  dplyr::filter(travel_speed_val == aux_spd)        # by random speed



# Check if is only one run (seed) and speed val:
results_unnest_turtles$`random-seed` %>% unique()
results_unnest_turtles$travel_speed_val %>% unique()

# Plot
gua.plot.general <- gua.sf +
  geom_path(data = results_unnest_turtles,
            aes(x = x, y = y),
            size = 0.15) +
  geom_point(data = results_unnest_turtles,
             aes(x = x, y = y
                 , group = behavior,
                 color = behavior,
                 shape = behavior
                 ),
             size = 1.4) +
  scale_color_manual(values = simulated_colors) +
  scale_shape_manual(values = simulated_shapes) +
  ggtitle(paste0("Guareí - simulated (1 run, 10 days - All resources); speed_val = ", aux_spd))
gua.plot.general

```

#### One day of one random run (1 random seed) (= next_day button) all steps and each 10 steps

```{r}
# To keep the original object without modifications:
results_unnest_turtles <- results_unnest

# Select random run by selecting random seed (run of x days = seed)
aux_run <- results_unnest$`random-seed` %>%
  na.exclude() %>%
  sample(size = 1)

# Select random speed as above
aux_spd <- results_unnest$travel_speed_val %>%
  na.exclude() %>%
  sample(size = 1)

# Select random day after selecting the same random seed as above
aux <- results_unnest %>% 
  filter(`random-seed` == aux_run) %>% 
    dplyr::select(day)
aux_day <- aux$day %>%
  na.exclude() %>%
  sample(size =  1)


# All steps
results_unnest_turtles_allsteps <- results_unnest_turtles %>%
  dplyr::filter(agent=="turtles") %>%               # by agent
  dplyr::filter(`random-seed` == aux_run) %>%       # by random run (~= number of the agent = who)
  dplyr::filter(travel_speed_val == aux_spd) %>%    # by random speed_val
  dplyr::filter(`day` == aux_day)                   # by random day
  # dplyr::filter(`timestep` %in% seq(8, 108, by=10)) # each 10 steps

gp1 <- gua.sf +
  # facet_wrap(~timestep) + # , ncol=6, nrow = 2
  # coord_equal() +
  geom_path(data = results_unnest_turtles_allsteps,
            aes(x = x, y = y), 
            size = 0.15) +
  geom_point(data = results_unnest_turtles_allsteps,
             aes(x = x, y = y, group = behavior,
                 color = behavior,
                 shape = behavior
                 ), size = 2.2) +
  scale_color_manual(values = simulated_colors) +
  scale_shape_manual(values = simulated_shapes) + 
  ggtitle(paste("Output map of all simulation\nticks (one day); speed_val = ", aux_spd))
gp1

# ggsave(filename = "setup-for-workflow-simple_multiple-layers.png",
       # dpi = 300, width = 30, height = 20, units = "cm")



# Each 10 steps

results_unnest_turtles_by10 <- results_unnest %>%
  dplyr::filter(agent=="turtles") %>%               # by agent
  dplyr::filter(`random-seed` == aux_run) %>%       # by random run (~= number of the agent = who)
  dplyr::filter(travel_speed_val == aux_spd) %>%    # by random speed_val
  dplyr::filter(`day` == aux_day) %>%               # by random day
  dplyr::filter(`timestep` %in% 
                  seq(8, 108, by=10) |              # each 10 steps AND
                  row_number(`timestep`)==n())      # last observation

gp2 <- gua.sf +
  # facet_wrap(~timestep) + # , ncol=6, nrow = 2
  # coord_equal() +
  geom_path(
    data = results_unnest_turtles_allsteps,
            aes(x = x, y = y), # , group = behavior, color = behavior
            size = 0.15) +
   geom_point(
     data = results_unnest_turtles_by10,
             aes(x = x, y = y, group = behavior,
                 color = behavior,
                 shape = behavior
                 ),
             size = 2.2) +
  scale_color_manual(values = simulated_colors) +
  scale_shape_manual(values = simulated_shapes) +
  ggtitle(paste("Output map of each 10th and last simulation\ntick (one day); speed_val = ", aux_spd))
gp2

# ggsave(filename = "setup-for-workflow-simple_multiple-layers.png",
       # dpi = 300, width = 30, height = 20, units = "cm")
```


#### Various runs (showing sleeping sites)

```{r}
# turtles (only last step)
results_unnest_routes <- results_unnest %>%
  dplyr::filter(agent=="turtles") %>%               # by agent
  dplyr::filter(`random-seed` == aux_run) %>%       # by random run (~= number of the agent = who)
  dplyr::group_by(travel_speed_val, day)            # by speed_val and days

results_unnest_laststeps  <-  results_unnest_routes %>% 
  dplyr::slice(tail(row_number(), 1))               # 10 for last 10 steps

# last step + frugivory points
results_unnest_gp3 <- results_unnest %>%
  dplyr::filter(agent=="turtles") %>%               # by agent
dplyr::filter(`random-seed` == aux_run) %>%         # by random run (~= number of the agent = who)
  dplyr::group_by(travel_speed_val, day) %>%        # by speed_val and days
  dplyr::filter(behavior == "frugivory") %>%        # frugivory records
  dplyr::bind_rows(results_unnest_laststeps)

gp3 <- gua.sf +
  facet_wrap(~travel_speed_val, ncol = 4) + # , ncol=6, nrow = 2
  # coord_equal() +
  geom_path(
    data = results_unnest_routes,
            aes(x = x, y = y), # , group = behavior, color = behavior
            size = 0.15) +
   geom_point(
     data = results_unnest_gp3,
             aes(x = x, y = y, group = behavior,
                 color = behavior,
                 shape = behavior
                 ),
             size = 1.8) +
  scale_color_manual(values = simulated_colors) +
  scale_shape_manual(values = simulated_shapes) +
  ggtitle("Output map of one random 10 d run for each travel_speed_val")
gp3

# ggsave(filename = here("Model_analysis", "Workflow", "Run_travelspeedvar",
#                        "Output-map-of-10d-runs-for-each-speedval.png"),
#        dpi = 300, width = 30, height = 20, units = "cm")

```


***

\pagebreak

## Validation Patterns

We are not checking seed dispersal patterns now, just movement and ranging patterns.

Load data of all other groups that are being used for validation
```{r}
## using original datasets from each person
dat.gua.orig <- read.csv2("D:/Data/Documentos/github/BLT-Movement-Patterns/asltraj/Data_Guarei_FelipeBufalo_EMZ1.csv",
                          dec = ".", stringsAsFactors = TRUE)
# Last version of Santa Maria:
# dat.sma.orig <- read.csv2(here("D:/Data/Documentos/github/BLT-Movement-Patterns/asltraj/ltraj_df_Data_Sma_EMZ6_outofsight.csv"), 
#                           dec = ".", stringsAsFactors = TRUE)
# interpolated data (DPL function can't take NAs):
dat.sma.orig <- read.csv2(here("D:/Data/Documentos/github/BLT-Movement-Patterns/asltraj/ltraj_df_Data_Sma_EMZ5.csv"), 
                          dec = ".", stringsAsFactors = TRUE)
dat.suz.orig <- read.csv2(here("D:/Data/Documentos/github/BLT-Movement-Patterns/asltraj/Data_Suzano_Anne_EMZ4.csv"), 
                          dec = ".", stringsAsFactors = TRUE)
dat.taq.orig <- read.csv2(here("D:/Data/Documentos/github/BLT-Movement-Patterns/asltraj/Data_PEMDTaquara_Anne_EMZ4.csv"), 
                          dec = ".", stringsAsFactors = TRUE)

## Change POSIXct collum to date type with lubridate package and define id (animal id)
# Obs: there's already a column called "id" in each dataset, we are just making it more readable.

dat.gua <- dat.gua.orig %>%
  rename(datetime = POSIXct) %>% 
  mutate(datetime = lubridate::ymd_hms(datetime))
dat.gua <- dat.gua %>% 
  mutate(id = "Guareí") %>% 
  dplyr::select("x", "y", "datetime", "id", "behavior")

dat.sma <- dat.sma.orig %>%
  rename(datetime = POSIXct) %>% 
  mutate(datetime = lubridate::ymd_hms(datetime))
dat.sma <- dat.sma %>% 
  mutate(id = "Santa Maria") %>% 
  dplyr::select("x", "y", "datetime", "id", "behavior")

dat.suz <- dat.suz.orig %>%
  rename(datetime = POSIXct) %>% 
  mutate(datetime = lubridate::ymd_hms(datetime))
dat.suz <- dat.suz %>% 
  mutate(id = "Suzano") %>% 
  # rename(x = X,
  #        y = Y) %>% 
  dplyr::select("x", "y", "datetime", "id", "behavior")

dat.taq <- dat.taq.orig %>%
  rename(datetime = POSIXct) %>% 
  mutate(datetime = lubridate::ymd_hms(datetime))
dat.taq <- dat.taq %>% 
  mutate(id = "Taquara") %>% 
  dplyr::select("x", "y", "datetime", "id", "behavior")
```

Lets bind all the empirical data together with the simulated data
```{r}
df <- rbind(
  dat.gua,
  dat.sma,
  dat.taq,
  dat.suz
) %>%
  mutate(`random-seed` = "Empirical") %>%
  mutate(travel_speed_val = "Empirical") %>% 
  mutate(behavior = recode(behavior, 
                           "for" = "foraging",
                           "feed_fruits" = "frugivory")) %>% 
  mutate(day = lubridate::day(datetime)) %>% 
  mutate(month = lubridate::month(datetime, label = T, abbr = T, 
                                  locale="English_United States")) %>% 
  mutate(year = lubridate::year(datetime)) %>% 
  mutate(mm_yyyy = paste0(month, "/", year)) %>% 
  mutate(dd_mm_yyyy = paste0(day, "/", month, "/", year)) %>% 
  dplyr::select(-c("day", "year"))

# str(dat.all)

## And then include the simulation data
# dat.all <- dat.all %>% 
#   rename(timestep = datetime)

df$datetime <- as.character(df$datetime) 

sim_gua <- results_unnest %>% 
  rename(datetime = timestep) %>% # make timestep = datetime
  mutate(datetime = paste0("Sim_day", day)) %>% 
  # mutate(id = paste0("Guareí_", `random-seed`)) %>% 
  mutate(id = "Guareí - Simulated") %>% 
  dplyr::select("x", "y", "datetime", "id", "random-seed", "travel_speed_val", "behavior") %>% 
  mutate(mm_yyyy = "All_months") %>% # because the simulation was carried using trees of every month
  mutate(dd_mm_yyyy = paste0(datetime, "/", mm_yyyy)) %>%  # because the simulation was carried using trees of every month
  mutate(month = "All months")

dat.all <- rbind(
  df, 
  sim_gua
)

dat.all <- dat.all %>% 
  mutate(datetime = as_factor(datetime))

# dat.all$id %>% unique()

# Alter group order:
# dat.all <- dat.all %>% 
#    mutate(id = factor(id, levels = c(
#                            "Suzano", "Santa Maria", "Taquara",
#                            "Guareí", "Simulated")
#                            ))
                           
# dat.all$id %>% unique()
```


### Dayly Path Lenght (DPL)

Calculate and plot DPL
```{r DPL function, echo = FALSE }
dpl <- function(df) {
  dist_list <- numeric()
  dist <- numeric()
  for (df in split(df, df$day)) {
    dist <- 0
    for (i in 2:nrow(df)) {
      dist <- dist + sqrt((df$x[i] - df$x[i - 1]) ^ 2 +
                            (df$y[i] - df$y[i - 1]) ^ 2)
    }
    dist_list <- c(dist_list, dist)
  }
  return(dist_list)
}
```

```{r, echo=FALSE}
dpl_gua_jul <- dpl(df = dat.gua.orig.jul)

avg_dist_jul <- mean(dpl_gua_jul)
sd_dist_jul <- sd(dpl_gua_jul)
# paste("Empirical (July, 6 days) Mean DPL (m)", round(avg_dist, 2))
# paste("Empirical (July, 6 days) DPL sd", round(sd_dist, 2))

dat.gua.all <- dat.gua.orig %>% 
  rename(day = date) # %>% 
  # rename(day = burst)
dpl_gua <- dpl(df = dat.gua.all)

avg_dist <- mean(dpl_gua)
sd_dist <- sd(dpl_gua)

dpl_sim <- dpl(df = results_unnest)

avg_dist_sim <- mean(dpl_sim)
sd_dist_sim <- sd(dpl_sim)
# paste("Simulated (July, 30 days) Mean DPL (m)", round(avg_dist_sim, 2))
# paste("Simulated (July, 30 days) DPL sd", round(sd_dist_sim, 2))

# loc_tam_lastdays <- results_unnest %>% filter(day > 10) 
# dpl_sim_lastdays <-results_unnest %>% dpl()

# avg_dist_sim_lastdays <- mean(dpl_sim_lastdays)
# sd_dist_sim_lastdays <- sd(dpl_sim_lastdays)
# paste("Simulated (July, 20 days) Mean DPL (m) after burn-in run of 10 days", round(avg_dist_sim_lastdays, 2))
# paste("Simulated (July, 20 days) DPL sd after burn-in run of 10 days", round(sd_dist_sim_lastdays, 2))
```


```{r, echo=F}
# par(xpd=TRUE)
# par(oma=c(0,0,0,0))
# par(mar=c(4,4,2,1))
# par(mfrow=c(3,1))
# 
# 
# hist <- hist_f(x=dpl_gua_jul,
#      main = "Empirical (July, 6 days)",
#      xlab = ""
#      )
# abline(v=avg_dist_jul, col="red", lty=2)
# text(x=avg_dist_jul, y=max(hist$counts)
#    , sprintf("sd = %7.2f", sd_dist_jul)
#    , adj = c(0, 0))
# text(x=avg_dist_jul, y=max(hist$counts)
#    , sprintf("mean = %7.2f", avg_dist_jul)
#    , col = "red"
#    , adj = c(0, -1.2))
# 
# 
# hist <- hist_f(x=dpl_gua,
#              main="Empirical (All months, 28 days)",
#              xlab=""
#      )
# abline(v=avg_dist, col="red", lty=2)
# text(x=avg_dist, y=max(hist$counts)
#    , sprintf("sd = %7.2f", sd_dist)
#    , adj = c(0, 0))
# text(x=avg_dist, y=max(hist$counts)
#    , sprintf("mean = %7.2f", avg_dist)
#    , col = "red"
#    , adj = c(0, -1.2))
# 
# 
# hist <- hist_f(x=dpl_sim,
#              main="Simulated (All resources, 10 days)",
#              xlab = "Daily Path Length (m)"
#      )
# abline(v=avg_dist_sim, col="red", lty=2)
# text(x=avg_dist_sim, y=max(hist$counts)
#    , sprintf("sd = %7.2f", sd_dist_sim)
#    , adj = c(0, 0))
# text(x=avg_dist_sim, y=max(hist$counts)
#    , sprintf("mean = %7.2f", avg_dist_sim)
#    , col = "red"
#    , adj = c(0, -1.2))
# 

```

Calculate DPL
```{r}
df <- dat.all

dpl <- function(df) {
  # options(stringsAsFactors=TRUE)
  dist_list <- data.frame(Group = "",  DPL = -1, Seed = "", TravelSpeed = -1, Day = "", Month = "")
  dist <- numeric()
  # group <- numeric()
  # seed <- numeric()
  for (group in unique(df$id)) {
    df3 <- df[df$id == group, ]
    for (seed in unique(df3$`random-seed`)) {
      df4 <- df3[df3$`random-seed` == seed, ]
      for (vel in unique(df4$travel_speed_val)) {
      df5 <- df4[df4$travel_speed_val == vel, ]
  
      for (df6 in split(df5, df5$dd_mm_yyyy)) {
          dist <- 0
          for (i in 2:nrow(df6)) {
           dist <- dist + sqrt((df6$x[i] - df6$x[i - 1]) ^ 2 +
                                  (df6$y[i] - df6$y[i - 1]) ^ 2)
         }
         dist_list <- rbind.data.frame(dist_list, 
                                       c(group, dist, df6$`random-seed`[1], df6$travel_speed_val[1],
                                          df6$dd_mm_yyyy[1], as.character(df6$month[1])),
                             stringsAsFactors = TRUE)
       }
      }
    }
  }
  dist_list <- dist_list[-1, ]
  dist_list <- as.data.frame(dist_list)
  # colnames(dist_list) <- c("Group", "DPL", "Day", "Time_frame", "Month")
  dist_list$DPL <- as.numeric(dist_list$DPL)
  dist_list <- dist_list %>% mutate_if(is.character, as.factor)
  return(dist_list)
}


dpl_all <- dpl(df = df)

# Reorder groups
dpl_all <- dpl_all %>%
  mutate(Group = factor(Group, levels = c(
                           "Suzano", "Santa Maria", "Taquara",
                           "Guareí", "Guareí - Simulated"),
                        labels = c(
                           "Suzano", "Santa Maria", "Taquara",
                           "Guareí", "Guareí - Simulated"
                        )))
# str(dpl_all)
# 
# dpl_all$Group %>% unique()
# dpl_all$Group %>% levels()
# dpl_all$Seed %>% unique()
# dpl_all$TravelSpeed %>% unique()


```


Plot DPL (All areas) ggplot
```{r}
dpl_all %>% 
  # group_by(Group, Seed, TravelSpeed) %>% 
  # facet_wrap(~Seed) +
  ggplot(aes(x = Group, y = DPL, color = TravelSpeed)) +
  geom_boxplot() +
  guides(fill=FALSE) +
  # geom_jitter(width = 0.15) +
  ylab("DPL (m)")  #+
  # annotate("text", x=2, y=5000, label= paste0("Mean ± sd = ", round(avg_dist, 2), " ± ", round(sd_dist, 2)))
  # ggtitle()

# ggsave(filename = here("Model_analysis", "Workflow", "Run_travelspeedvar",
#                        "DPL-speedval.png"),
#        dpi = 300, width = 30, height = 20, units = "cm")

```

By Month
```{r}
dpl_all %>% 
  ggplot(aes(x = Group, y = DPL, color = Month)) +
  geom_boxplot() +
  guides(fill=FALSE) +
  ylab("DPL (m)") 
# +
#   geom_jitter(width = 0.15)
  # ggtitle()

# ggsave(filename = here("Model_analysis", "Workflow", "Run_travelspeedvar",
#                        "DPL-speedval-by-month.png"),
#        dpi = 300, width = 30, height = 20, units = "cm")

```

\pagebreak

### Home Range

Comparison between methods: https://doi.org/10.1111/2041-210X.13786

# Signer & Fieberg 2021 (didn't work)
```{r}
library("amt")
dat.all %>% 
  make_track(x, y, datetime, id = id
             # , crs = 5070
             )

a <- dat.all %>% 
  # dplyr::nest_by(data=-c(id, `random-seed`, travel_speed_val))
  dplyr::nest_by(data=c(x, y, datetime, behavior))
```

# With kernelUD()
Prepare dataframe for creating SpatialDataFrame
```{r, warnigs=F, message=F}
# setwd("D:/Data/Documentos/github/BLT-Movement-Patterns/Ranging-Patterns")

sim_gua_spdf <- sim_gua %>% 
  mutate(id_spdf = paste(id, `random-seed`, travel_speed_val))

pts_gua <- SpatialPointsDataFrame(dat.gua[ , c('x','y')], 
                              data.frame(dat.gua[ , c('id')]),
                              proj4string = CRS("+proj=utm +zone=22K +south +datum=WGS84 +unit=m +no_defs"))

# _EMZ6.csv Does not work because contains NA, but EMZ5 (this version) is interpolated (without NA):
pts_sma <- SpatialPointsDataFrame(dat.sma[ , c('x','y')],
                              data.frame(dat.sma[ , c('id')]),
                              proj4string = CRS("+proj=utm +zone=22K +south +datum=WGS84 +unit=m +no_defs"))

pts_taq <- SpatialPointsDataFrame(dat.taq[ , c('x','y')], 
                              data.frame(dat.taq[ , c('id')]),
                              proj4string = CRS("+proj=utm +zone=22K +south +datum=WGS84 +unit=m +no_defs"))

pts_suz <- SpatialPointsDataFrame(dat.suz[ , c('x','y')], 
                              data.frame(dat.suz[ , c('id')]),
                              proj4string = CRS("+proj=utm +zone=22K +south +datum=WGS84 +unit=m +no_defs"))

pts_sim_gua <- SpatialPointsDataFrame(sim_gua_spdf[ , c('x','y')], 
                              data.frame(sim_gua_spdf[ , c('id_spdf')]),
                              proj4string = CRS("+proj=utm +zone=22K +south +datum=WGS84 +unit=m +no_defs"))


plot(pts_gua)
plot(pts_taq)
plot(pts_suz)
# plot(pts_sim_gua)


pts_all <- SpatialPointsDataFrame(dat.all[ , c('x','y')], 
                              data.frame(dat.all[ , c('travel_speed_val', 
                                                      'id', 'random-seed')]),
                              proj4string = CRS("+proj=utm +zone=22K +south +datum=WGS84 +unit=m +no_defs"))
# plot(pts_all)

```

Calculate KernelUD
```{r}
t_gua <- kernelUD(pts_gua[ , 1], h = "href", kern = 'bivnorm', grid = 400, same4all = T)
t_sma <- kernelUD(pts_sma[ , 1], h = "href", kern = 'bivnorm', grid = 400, same4all = T)
t_taq <- kernelUD(pts_taq[ , 1], h = "href", kern = 'bivnorm', grid = 400, same4all = T)
t_suz <- kernelUD(pts_suz[ , 1], h = "href", kern = 'bivnorm', grid = 400, same4all = T)
t_sim_gua <- kernelUD(pts_sim_gua[ , 1], h = "href", kern = 'bivnorm', grid = 400, same4all = T)

# Plot volume countours
vud_gua <- getvolumeUD(t_gua)
xyzv <- as.image.SpatialGridDataFrame(vud_gua[[1]])
contour(xyzv) # , add=TRUE

vud_sma <- getvolumeUD(t_sma)
xyzv <- as.image.SpatialGridDataFrame(vud_sma[[1]])
contour(xyzv) # , add=TRUE

vud_taq <- getvolumeUD(t_taq)
xyzv <- as.image.SpatialGridDataFrame(vud_taq[[1]])
contour(xyzv) # , add=TRUE

vud_suz <- getvolumeUD(t_suz)
xyzv <- as.image.SpatialGridDataFrame(vud_suz[[1]])
contour(xyzv) # , add=TRUE

# vud_sim_gua <- getvolumeUD(t_sim_gua)
# xyzv <- as.image.SpatialGridDataFrame(vud_sim_gua[[1]])
# contour(xyzv) # , add=TRUE

image(t_gua)

ka_gua <- kernel.area(t_gua, percent = seq(10, 95, by = 5), unin = "m", unout = "ha")
ka_sma <- kernel.area(t_sma, percent = seq(10, 95, by = 5), unin = "m", unout = "ha")
ka_suz <- kernel.area(t_suz, percent = seq(10, 95, by = 5), unin = "m", unout = "ha")
ka_taq <- kernel.area(t_taq, percent = seq(10, 95, by = 5), unin = "m", unout = "ha")
ka_sim_gua <- kernel.area(t_sim_gua, percent = seq(10, 95, by = 5), unin = "m", unout = "ha")

# par(mfrow=c(2,2))
plot(ka_taq)
plot(ka_suz)
plot(ka_gua)
plot(ka_sma)
plot(ka_sim_gua)

# # Tentando fazer uns subsets (nao funcionou):
# hr1 <- as.data.frame(ka_sim_gua)
# hr1 <- hr1 %>% mutate(HR_level = row.names(hr1))
# 
# hr1_gua <- hr1 %>% pivot_longer(c(1:5), names_to = "ID", values_to = "HR_value")
# # hr1_gua %>% group_by(ID, as_factor(HR_level)) %>% 
# #   summarise()
# hr1_gua %>% group_by(HR_level) %>% 
#   summarise(meanHR = mean(HR_value),
#             sdHR = sd(HR_value))
# 
# plot(hr1_gua)

```

### 95% Kernel (home range)

```{r}
k95_gua <- getverticeshr(t_gua, percent = 95, unin = "m", unout = "ha")
# as.data.frame(k95_gua)
plot(k95_gua, col = rainbow(7, alpha = 0.5))
# plot(pts_gua) #, pch=16, col = dat.gua$id, cex=0.1, add=T)

k95_sma <- getverticeshr(t_sma, percent = 95, unin = "m", unout = "ha")
# as.data.frame(k95_gua)
plot(k95_sma, col = rainbow(7, alpha = 0.5))
# plot(pts_gua) #, pch=16, col = dat.gua$id, cex=0.1, add=T)

k95_suz <- getverticeshr(t_suz, percent = 95, unin = "m", unout = "ha")
# as.data.frame(k95_suz)
plot(k95_suz, col = rainbow(7, alpha = 0.5))
# plot(pts_suz) #, pch=16, col = dat.gua$id, cex=0.1, add=T)


k95_taq <- getverticeshr(t_taq, percent = 95, unin = "m", unout = "ha")
# as.data.frame(k95_taq)
plot(k95_taq, col = rainbow(7, alpha = 0.5))
# plot(pts_taq) #, pch=16, col = dat.gua$id, cex=0.1, add=T)

k95_sim_gua <- getverticeshr(t_sim_gua, percent = 95, unin = "m", unout = "ha")
# as.data.frame(k95_sim_gua)
plot(k95_sim_gua, col = rainbow(7, alpha = 0.5))
# plot(k95_sim_gua[[1]][[1]], col = rainbow(7, alpha = 0.5))
# plot(pts_sim_gua) #, pch=16, col = dat.gua$id, cex=0.1, add=T)


#
# str(k95_sim_gua)
# k95_sim_gua_sf <- st_as_sf(k95_sim_gua)
# 
# plot(k95_sim_gua_sf[k95_sim_gua_sf == "Guareí_-1062115611", ])
# k95_sim_gua_sf$geometry #[[1]]
# 
# str(k95_sim_gua_sf)


# Put all together:
hr_values95 <- as.data.frame(k95_gua)
hr_values95 <- rbind(hr_values95, as.data.frame(k95_sma))
hr_values95 <- rbind(hr_values95, as.data.frame(k95_suz))
hr_values95 <- rbind(hr_values95, as.data.frame(k95_taq))
hr_values95 <- rbind(hr_values95, as.data.frame(k95_sim_gua))

row.names(hr_values95) <- NULL

# pat1 <- "(\\d)+"
# pat2 <- " (\\d)+$"
# pat2 <- "(\\d)+$"
# pat3 <- "[:digit:]{1}$"
# pat4 <- "r'(?<!\S)\d+\.\d+(?!\S)'"
pat4 <- "(?>-)*[[:digit:]]+\\.*[[:digit:]]*" 
pat5 <- "(?>-)*[[:digit:]]+\\.*[[:digit:]]*$" 

hr_values95 <- hr_values95 %>%
  mutate(nome1 = stringr::word(id, 1)) %>% 
  mutate(nome2 = "Simulated") %>% 
  mutate(seed = str_extract(id, pat4)) %>%    # pega as seeds negativas
  mutate(TravelSpeed = str_extract(id, pat5)) # pega os valores de travel speed

hr_values95$nome1[2] <- "Santa Maria"
hr_values95$nome2[1:4] <- ""
hr_values95$seed[1:4] <- "Empirical"
hr_values95$TravelSpeed[1:4] <- "Empirical"

hr_values95 <- hr_values95 %>%   
  mutate(Group = paste(nome1, nome2)) %>%
  mutate(Group = str_trim(Group, side = "both")) %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(KDE_95 = area) %>% 
  dplyr::select("Group", "seed", "TravelSpeed", "KDE_95")

# str(hr_values)
```

### 50% Kernel (core area)
```{r}
k50_gua <- getverticeshr(t_gua, percent = 50, unin = "m", unout = "ha")
# as.data.frame(k50_gua)
plot(k50_gua, col = rainbow(7, alpha = 0.5))
# plot(pts_gua) #, pch=16, col = dat.gua$id, cex=0.1, add=T)

k50_sma <- getverticeshr(t_sma, percent = 50, unin = "m", unout = "ha")
# as.data.frame(k50_gua)
plot(k50_sma, col = rainbow(7, alpha = 0.5))
# plot(pts_gua) #, pch=16, col = dat.gua$id, cex=0.1, add=T)

k50_suz <- getverticeshr(t_suz, percent = 50, unin = "m", unout = "ha")
# as.data.frame(k50_suz)
plot(k50_suz, col = rainbow(7, alpha = 0.5))
# plot(pts_suz) #, pch=16, col = dat.gua$id, cex=0.1, add=T)


k50_taq <- getverticeshr(t_taq, percent = 50, unin = "m", unout = "ha")
# as.data.frame(k50_taq)
plot(k50_taq, col = rainbow(7, alpha = 0.5))
# plot(pts_taq) #, pch=16, col = dat.gua$id, cex=0.1, add=T)

k50_sim_gua <- getverticeshr(t_sim_gua, percent = 50, unin = "m", unout = "ha")
# as.data.frame(k50_sim_gua)
plot(k50_sim_gua, col = rainbow(7, alpha = 0.5))
# plot(k50_sim_gua[[1]][[1]], col = rainbow(7, alpha = 0.5))
# plot(pts_sim_gua) #, pch=16, col = dat.gua$id, cex=0.1, add=T)


# Put all together:
hr_values50 <- as.data.frame(k50_gua)
hr_values50 <- rbind(hr_values50, as.data.frame(k50_sma))
hr_values50 <- rbind(hr_values50, as.data.frame(k50_suz))
hr_values50 <- rbind(hr_values50, as.data.frame(k50_taq))
hr_values50 <- rbind(hr_values50, as.data.frame(k50_sim_gua))
hr_values50 <- hr_values50 %>% 
  mutate(KDE_50 = area)

hr_values <- cbind(hr_values95, hr_values50[ , 3])
colnames(hr_values)[5] <- "KDE_50"

# str(hr_values)
# hr_values$Group %>% levels()
# a$Group %>% levels()

# Reorder groups
hr_values <- hr_values %>%
  mutate(Group = factor(Group, levels = c(
                           "Suzano", "Santa Maria", "Taquara",
                           "Guareí", "Guareí Simulated")
                           ))
```

### Boxplot home ranges (All areas) ggplot
```{r}
# KDE 95

hr_values %>% 
  # group_by(Group, Seed, TravelSpeed) %>% 
  # facet_wrap(~Seed) +
  ggplot(aes(x = Group, y = KDE_95, color = TravelSpeed)) +
  geom_boxplot() +
  guides(fill=FALSE) +
  ylim(0, 350) +
  ylab("Area (ha)") +
  ggtitle("KDE 95% (Home range)")
  # geom_jitter(width = 0.15) +
  # annotate("text", x=2, y=5000, label= paste0("Mean ± sd = ", round(avg_dist, 2), " ± ", round(sd_dist, 2)))

# ggsave(filename = here("Model_analysis", "Workflow", "Run_travelspeedvar",
#                        "HomeRangeKDE95-speedval.png"),
#        dpi = 300, width = 30, height = 20, units = "cm")


# KDE 50
hr_values %>% 
  # group_by(Group, Seed, TravelSpeed) %>% 
  # facet_wrap(~Seed) +
  ggplot(aes(x = Group, y = KDE_50, color = TravelSpeed)) +
  geom_boxplot() +
  ylim(0, 350) +
  guides(fill=FALSE) +
  # geom_jitter(width = 0.15) +
  ylab("")  +
   ggtitle("KDE 50% (Core area)")
  # annotate("text", x=2, y=5000, label= paste0("Mean ± sd = ", round(avg_dist, 2), " ± ", round(sd_dist, 2)))
  # ggtitle()

# ggsave(filename = here("Model_analysis", "Workflow", "Run_travelspeedvar",
#                        "HomeRangeKDE50-speedval.png"),
#        dpi = 300, width = 30, height = 20, units = "cm")


```


### Saving the shape file for further use

```{r}
#datadir <- "directory\\k50.gpkg"
#rgdal::writeOGR(k50,datadir, layer = "k50.gpkg", driver = "GPKG")
```


\pagebreak

### Activity budget

Summarize activity budget
```{r}
dat.all <- dat.all %>%
  mutate(Group = id)

dat.summary <- dat.all %>% 
  group_by(Group) %>%
  mutate(n_total = n()) %>% 
  group_by(Group, behavior) %>% 
  mutate(n_obs = n()) %>% 
  mutate(activity_budget = (n_obs/n_total)*100 ) %>% 
  mutate(TravelSpeed = travel_speed_val) %>% 
  dplyr::select(c(Group, behavior, TravelSpeed, activity_budget)) %>% 
  unique() %>%
  # drop_na() %>% 
  ungroup() 

# Reorder groups
dat.summary <- dat.summary %>%
  mutate(Group = factor(Group, levels = c(
                           "Suzano", "Santa Maria", "Taquara",
                           "Guareí", "Guareí - Simulated")
                           ))

# dat.summary$Group %>% levels()
# str(dat.summary)
```

Plot activity budget ALL behaviors (wrong)
```{r}
dat.summary %>% 
  ggplot(aes(x = interaction(Group, TravelSpeed), y = activity_budget, fill = behavior)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

dat.summary %>% 
  ggplot(aes(x = interaction(Group, TravelSpeed), y = activity_budget, fill = behavior)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

```{r}
## Plot activity budget main 4 behaviors
act_bug_4 <- dat.summary %>%
  dplyr::filter(behavior %in% c("resting", "travel", "foraging", "frugivory")) %>% 
  droplevels() 

p1 <- act_bug_4 %>% 
  ggplot(aes(x = interaction(Group, TravelSpeed), y = activity_budget, fill = behavior)) +
  geom_bar(stat = "identity", position = "fill") +
  ggtitle("Activity budget of 4 behaviors") +
  ylab("Proportion (%)") +
  xlab("")  +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

p1

## Plot activity budget main 4 behaviors + others
act_bug_5 <- dat.all %>% 
  mutate(behavior = recode(behavior,
                           "agonistic" = "others",
                           "feed_gum" = "others",
                           # "" = "others",
                           "long_call" = "others",
                           "outofsight" = "others",
                           "rubbing" = "others",
                           "sleeping" = "others",
                           "intergroup_encounter" = "others",
                           "soc_int" = "others",
                           "idle" = "others"
  )) %>%
  group_by(Group) %>%
  mutate(n_total = n()) %>% 
  group_by(Group, behavior) %>% 
  mutate(n_obs = n()) %>% 
  mutate(activity_budget = (n_obs/n_total)*100 ) %>% 
  mutate(TravelSpeed = travel_speed_val) %>% 
  dplyr::select(c(Group, behavior, TravelSpeed, activity_budget)) %>% 
  unique() %>% 
  ungroup() %>% 
  filter(behavior != "")  %>%
  droplevels()


# # Reorder groups
# act_bug_5 <- act_bug_5 %>%
#   mutate(Group = factor(Group, levels = c(
#                            "Suzano Empirical", "Santa Maria Empirical", "Taquara Empirical",
#                            "Guareí Empírical"
#                            # , "Guareí - Simulated"
#                            )
#                            ))

act_bug_5$Group %>% levels()
act_bug_5$behavior %>% levels()

p2 <- act_bug_5 %>% 
  ggplot(aes(x = interaction(Group, TravelSpeed), y = activity_budget, fill = behavior)) +
  geom_bar(stat = "identity", position = "fill") +
  ggtitle("Activity budget of 4 behaviors + 'others'") +
  ylab("Proportion (%)") +
  xlab("") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

p2
```


### Turning Angles and Step Lenghts
```{r, include=FALSE}
dat.gua.orig.all <- dat.gua.orig
dat.gua.orig.all$id <- "Guareí Empirical"
dat.gua.orig.all$id <- as.factor(dat.gua.orig.all$id)
dat.gua.orig.all$dayfct <- as.factor(paste("Day ", dat.gua.orig.all$day))

dat.gua.orig.all_ltraj <- adehabitatLT::as.ltraj(xy = dat.gua.orig.all[, c("x", "y")], 
                                       id = dat.gua.orig.all$id,
                                       burst = dat.gua.orig.all$dayfct,
                                       proj4string = CRS(our_crs),
                                       typeII = FALSE,
                                       infolocs = dat.gua.orig.all[ , c("behavior", "dayfct")]
                                       )
# Type I (time not recorded) -> OK. Infolocs -> OK
dat.gua.orig.all_ltraj_df <- ld(dat.gua.orig.all_ltraj) # Transform to df


dat.gua.orig.jul$id <- "Guareí Empirical (July only, 6d)"
dat.gua.orig.jul$id <- as.factor(dat.gua.orig.jul$id)
dat.gua.orig.jul$dayfct <- as.factor(paste("Day ", dat.gua.orig.jul$day))

dat.gua.orig.jul_ltraj <- adehabitatLT::as.ltraj(xy = dat.gua.orig.jul[, c("x", "y")], 
                                       id = dat.gua.orig.jul$id,
                                       burst = dat.gua.orig.jul$dayfct,
                                       proj4string = CRS(our_crs),
                                       typeII = FALSE,
                                       infolocs = dat.gua.orig.jul[ , c("behavior", "dayfct")]
                                       )
# Type I (time not recorded) -> OK. Infolocs -> OK
dat.gua.orig.jul_ltraj_df <- ld(dat.gua.orig.jul_ltraj) # Transform to df


results_unnest$id <-  "Guareí Simulated" 
results_unnest$id <- as.factor(results_unnest$id)
results_unnest$dayfct <- as.factor(paste("Day ", results_unnest$day))

results_unnest_ltraj <- adehabitatLT::as.ltraj(xy = results_unnest[, c("x", "y")], 
                                       id = results_unnest$id,
                                       burst = results_unnest$dayfct,
                                       proj4string = CRS(our_crs),
                                       typeII = FALSE,
                                       infolocs = results_unnest[ , c(1:3, 6, 8:10)]
                                       )
# Type I (time not recorded) -> OK. Infolocs -> OK
results_unnest_ltraj_df <- ld(results_unnest_ltraj) # Transform to df

```

```{r Mean step lenght and turning angles, warning=FALSE, echo=F, include=F}
# mean rel angle (degrees)
# paste("Empirical (July, 6 d) Mean Relative Angle (degrees) = ", 
#       dat.gua.orig.jul_ltraj_df$rel.angle %>%
#         mean(na.rm = T) %>% round(2))
# 
# paste("Simulated (July, 30 d) Mean Relative Angle (degrees)", 
#       loc_tam_ltraj_df$rel.angle %>%
#         mean(na.rm = T )%>% round(2))
#       
# paste("Simulated (July, 20 d, after burn-in run of 10 days) Mean Relative Angle (degrees)", 
#       loc_tam_lastdays_ltraj_df$rel.angle %>%
#         mean(na.rm = T) %>% round(2))

# mean rel angle (radians)
# dat.gua.orig.jul_ltraj_df$rel.angle.rad <- dat.gua.orig.jul_ltraj_df$rel.angle * (180 / pi)
# loc_tam_ltraj_df$rel.angle.rad <- loc_tam_ltraj_df$rel.angle * (180 / pi)
# loc_tam_lastdays_ltraj_df$rel.angle.rad <- loc_tam_lastdays_ltraj_df$rel.angle * (180 / pi)
# 
# dat.gua.orig.jul_ltraj_df_ra_mean <- dat.gua.orig.jul_ltraj_df$rel.angle.rad %>%  mean(na.rm = TRUE)
# loc_tam_ltraj_df_ra_mean <- loc_tam_ltraj_df$rel.angle.rad %>% mean(na.rm = TRUE)
# loc_tam_lastdays_ltraj_df_ra_mean <- loc_tam_lastdays_ltraj_df$rel.angle.rad %>% mean(na.rm = TRUE)
# 
# paste("Mean Relative Angle (degrees) :", dat.gua.orig.jul_ltraj_df_ra_mean)
# paste("Mean Relative Angle (degrees) :", loc_tam_ltraj_df_ra_mean)
# paste("Mean Relative Angle (degrees) :", loc_tam_lastdays_ltraj_df_ra_mean)
# 
# 
# # mean step lenght
# paste("Mean Step lenght (meters) :", dat.gua.orig.jul_ltraj_df$dist %>% mean(na.rm = T))
# paste("Mean Step lenght (meters) :", loc_tam_ltraj_df$dist %>% mean(na.rm = T))
# paste("Mean Step lenght (meters) :", loc_tam_lastdays_ltraj_df$dist %>% mean(na.rm = T))
```

```{r Plot Step lenght + turnig angles, echo=F, warning=FALSE}
# Plot Step lengh
par(mfrow=c(1,3))
graphics::hist(dat.gua.orig.all_ltraj_df$dist, 
               breaks=50,
               xlim = c(0, 400), ylim = c(0, 1000),
               xlab = "Step length (m)", main = "\nEmpirical (All days)") %>%
  abline(v = mean(dat.gua.orig.all_ltraj_df$dist, na.rm = TRUE), col = "red", lwd = 3)
  text(200, 400, paste("mean = ", round(mean(dat.gua.orig.all_ltraj_df$dist, na.rm = TRUE), 2), 
                      " m"), cex = 1.4)
  
graphics::hist(dat.gua.orig.jul_ltraj_df$dist, 
               breaks=50,
               xlim = c(0, 400), ylim = c(0, 1000),
               xlab = "Step length (m)", main = "\nEmpirical (July, 6 d)")  %>%
  abline(v = mean(dat.gua.orig.jul_ltraj_df$dist, na.rm = TRUE), col = "red", lwd = 3)
  text(200, 400, paste("mean = ", round(mean(dat.gua.orig.jul_ltraj_df$dist, na.rm = TRUE), 2), 
                      " m"), cex = 1.4)
  
graphics::hist(results_unnest_ltraj_df$dist, 
               breaks=50,
               xlim = c(0, 400), ylim = c(0, 1000),
               xlab = "Step length (m)", main = "\nSimulated (All resources, 10 d)")  %>%
  abline(v = mean(results_unnest_ltraj_df$dist, na.rm = TRUE), col = "red", lwd = 3)
  text(200, 400, paste("mean = ", round(mean(results_unnest_ltraj_df$dist, na.rm = TRUE), 2), 
                      " m"), cex = 1.4)


# Plot Turning angles
par(mfrow=c(1,3))

circular::rose.diag(dat.gua.orig.all_ltraj_df$rel.angle, bins=30, prop=2.5, units = "degrees",
                    tol = 0, main = "\nEmpirical (All days)", cex = 1.2, shrink = 1.2, ticks = F)
circular::rose.diag(dat.gua.orig.jul_ltraj_df$rel.angle, bins=30, prop=2.5, units = "degrees", tol = 0,                      main = "\nSimulated (July, 6 d)", 
                    cex = 1.2, shrink = 1.2, ticks = F)
circular::rose.diag(results_unnest_ltraj_df$rel.angle, bins=30, prop=2.5, units = "degrees",
                    tol = 0, main = "\nSimulated (All resources, 10 d)",
                    cex = 1.2, shrink = 1.2, ticks = F)

```

\pagebreak

### Revisitations (coming soon)


***

\pagebreak

## F
